Supplemental Materials for\\ Quantifying Stability and Change in Personal Culture Using Panel Data

### 2023-09-28 supplementals/manuscript_supplementals.Rmd
changes in supplements.

---
title: |
  | Supplemental Materials for
  | Quantifying Stability and Change in Personal Culture Using Panel Data
author: 
- 
output:
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    toc: true
geometry: margin=1in 
mainfont: Times New Roman
fontsize: 12pt
header-includes:
  \usepackage{fontspec}
  \usepackage{longtable}
  \usepackage{multirow}
  \usepackage{array}
  \usepackage{booktabs}
  \usepackage{dcolumn}
  \usepackage{lscape}
  \usepackage{caption}
  \newcommand{\blandscape}{\begin{landscape}}
  \newcommand{\elandscape}{\end{landscape}}
---

@@

Table B1 presents the full set of coefficients from an OLS model regressing $\omega$ on multiple covariates, described in Figure 2 in the main manuscript.

```{=latex}
\begin{table}[ht]
\begin{center}
\caption*{Table B1: Regression Model} 
\label{tab:sometab}
\begin{tabular}{l c c}
\hline
 & Estimates & SE \\
\hline
N Part. (log)                                       & $0.01$        
                                                    & $(0.01)$      \\
Duration                                            & $-0.00$ 
                                                    & $(0.00)^{***}$ \\
N Waves (Part.)                                     & $0.00$        
                                                    & $(0.00)$      \\
N Waves (Survey)                                    & $-0.00$       
                                                    & $(0.00)$      \\
Wave 1 (Decade)                                     & $-0.01$  
                                                    & $(0.00)^{**}$  \\
Panels: BHPS                                        & $0.08$        
                                                    & $(0.05)$      \\
Panels: GSS                                         & $0.04$        
                                                    & $(0.05)$      \\
Panels: HILDA                                       & $0.08$        
                                                    & $(0.05)$      \\
Panels: PSID                                        & $0.09$    
                                                    & $(0.04)^{*}$  \\
Panels: SHP                                         & $0.06$        
                                                    & $(0.05)$      \\
Panels: SOEP                                        & $0.06$        
                                                    & $(0.05)$      \\
Panels: UKHLS                                       & $0.09$        
                                                    & $(0.06)$      \\
Topics: Environment and Climate                     & $0.04$   
                                                    & $(0.01)^{**}$      \\
Topics: Gender and Family                           & $0.00$        
                                                    & $(0.01)$      \\
Topics: Health and Morale                           & $0.03$   
                                                    & $(0.01)^{**}$      \\
Topics: National Identity, Ethnicity, Immigration   & $0.02$        
                                                    & $(0.01)$      \\
Topics: Occupation and Education                    & $-0.02$       
                                                    & $(0.02)$      \\
Topics: Religion and Spirituality                   & $-0.00$       
                                                    & $(0.01)$      \\
Topics: Social Life, Social Cohesion and Trust      & $0.03$  
                                                    & $(0.01)^{***}$      \\
Topics: Subjective SES                              & $0.03$    
                                                    & $(0.01)^{*}$      \\
\hline
Adjusted R$^2$                                      & $0.77$     &   \\
N                                                   & $609$      &  \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
\end{center}
\end{table}
```

>>>>

---
title: |
  | Supplemental Materials for
  | Quantifying Stability and Change in Personal Culture Using Panel Data
author: 
- 
output:
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    toc: true
geometry: margin=1in 
mainfont: Times New Roman
fontsize: 12pt
header-includes:
  \usepackage{fontspec}
  \usepackage{longtable}
  \usepackage{multirow}
  \usepackage{array}
  \usepackage{booktabs}
  \usepackage{dcolumn}
  \usepackage{lscape}
  \usepackage{siunitx}
  \usepackage{caption}
  \newcommand{\blandscape}{\begin{landscape}}
  \newcommand{\elandscape}{\end{landscape}}
---

@@

Table B1 presents the full set of coefficients from an OLS model regressing $\omega$ on multiple covariates, described in Figure 2. We multiplied the covariates by 100 to increase legibility.

```{=latex}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\newcommand\mc[1]{\multicolumn{1}{c}{#1}} % handy shortcut macro
\begin{table}[ht]
\begin{center}
\caption*{Table B1: Regression Model Estimating $\omega$}
\label{tab:sometab}
\begin{tabular}{l *{4}{d{1.2}} }
\hline
 & \mc{Estimates} & \mc{SE} \\
\hline
Number of Participants (Logged)                       & 0.99        
                                                      & 0.53      \\
Duration                                              & -0.49^{***} 
                                                      & 0.13      \\
Average Number of Waves Across Participants           & 0.09        
                                                      & 0.20      \\
Average Number of Waves per Item                      & -0.20       
                                                      & 0.23      \\
Wave 1 (Decade)                                       & -1.17^{**}  
                                                      & 0.44      \\
Panels: BHPS                                          & 0.08        
                                                      & 0.05      \\
Panels: GSS                                           & 0.04        
                                                      & 0.05      \\
Panels: HILDA                                         & 0.08        
                                                      & 0.05      \\
Panels: PSID                                          & 0.09^{*}    
                                                      & 0.04      \\
Panels: SHP                                           & 0.06        
                                                      & 0.05      \\
Panels: SOEP                                          & 0.06        
                                                      & 0.05      \\
Panels: UKHLS                                         & 0.09        
                                                      & 0.06      \\
Topics: Environment and Climate                       & 0.04^{**}   
                                                      & 0.01      \\
Topics: Gender and Family                             & 0.00        
                                                      & 0.01      \\
Topics: Health and Morale                             & 0.03^{**}   
                                                      & 0.01      \\
Topics: National Identity, Ethnicity and Immigration  & 0.02        
                                                      & 0.01      \\
Topics: Occupation and Education                      & -0.02       
                                                      & 0.02      \\
Topics: Religion and Spirituality                     & -0.00       
                                                      & 0.01      \\
Topics: Social Life, Social Cohesion and Trust        & 0.03^{***}  
                                                      & 0.01      \\
Topics: Subjective SES                                & 0.03^{*}    
                                                      & 0.01      \\
\hline
Adjusted R-Squared                                    & 0.77 &    \\
\hline
\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}. N = 609.}
\end{tabular}
\end{center}
\end{table}

### 2023-09-28 supplementals/manuscript_supplementals.tex
changes in supplements.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{fontspec} \usepackage{longtable} \usepackage{multirow} \usepackage{array} \usepackage{booktabs} \usepackage{dcolumn} \usepackage{lscape} \usepackage{caption} \newcommand{\blandscape}{\begin{landscape}} \newcommand{\elandscape}{\end{landscape}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

Table B1 presents the full set of coefficients from an OLS model
regressing \(\omega\) on multiple covariates, described in Figure 2 in
the main manuscript.

\begin{table}[ht]
\begin{center}
\caption*{Table B1: Regression Model} 
\label{tab:sometab}
\begin{tabular}{l c c}
\hline
 & Estimates & SE \\
\hline
N Part. (log)                                       & $0.01$        
                                                    & $(0.01)$      \\
Duration                                            & $-0.00$ 
                                                    & $(0.00)^{***}$ \\
N Waves (Part.)                                     & $0.00$        
                                                    & $(0.00)$      \\
N Waves (Survey)                                    & $-0.00$       
                                                    & $(0.00)$      \\
Wave 1 (Decade)                                     & $-0.01$  
                                                    & $(0.00)^{**}$  \\
Panels: BHPS                                        & $0.08$        
                                                    & $(0.05)$      \\
Panels: GSS                                         & $0.04$        
                                                    & $(0.05)$      \\
Panels: HILDA                                       & $0.08$        
                                                    & $(0.05)$      \\
Panels: PSID                                        & $0.09$    
                                                    & $(0.04)^{*}$  \\
Panels: SHP                                         & $0.06$        
                                                    & $(0.05)$      \\
Panels: SOEP                                        & $0.06$        
                                                    & $(0.05)$      \\
Panels: UKHLS                                       & $0.09$        
                                                    & $(0.06)$      \\
Topics: Environment and Climate                     & $0.04$   
                                                    & $(0.01)^{**}$      \\
Topics: Gender and Family                           & $0.00$        
                                                    & $(0.01)$      \\
Topics: Health and Morale                           & $0.03$   
                                                    & $(0.01)^{**}$      \\
Topics: National Identity, Ethnicity, Immigration   & $0.02$        
                                                    & $(0.01)$      \\
Topics: Occupation and Education                    & $-0.02$       
                                                    & $(0.02)$      \\
Topics: Religion and Spirituality                   & $-0.00$       
                                                    & $(0.01)$      \\
Topics: Social Life, Social Cohesion and Trust      & $0.03$  
                                                    & $(0.01)^{***}$      \\
Topics: Subjective SES                              & $0.03$    
                                                    & $(0.01)^{*}$      \\
\hline
Adjusted R$^2$                                      & $0.77$     &   \\
N                                                   & $609$      &  \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
\end{center}
\end{table}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{fontspec} \usepackage{longtable} \usepackage{multirow} \usepackage{array} \usepackage{booktabs} \usepackage{dcolumn} \usepackage{lscape} \usepackage{siunitx} \usepackage{caption} \newcommand{\blandscape}{\begin{landscape}} \newcommand{\elandscape}{\end{landscape}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

Table B1 presents the full set of coefficients from an OLS model
regressing \(\omega\) on multiple covariates, described in Figure 2. We
multiplied the covariates by 100 to increase legibility.

\newcolumntype{d}[1]{D{.}{.}{#1}}
\newcommand\mc[1]{\multicolumn{1}{c}{#1}} % handy shortcut macro
\begin{table}[ht]
\begin{center}
\caption*{Table B1: Regression Model Estimating $\omega$}
\label{tab:sometab}
\begin{tabular}{l *{4}{d{1.2}} }
\hline
 & \mc{Estimates} & \mc{SE} \\
\hline
Number of Participants (Logged)                       & 0.99        
                                                      & 0.53      \\
Duration                                              & -0.49^{***} 
                                                      & 0.13      \\
Average Number of Waves Across Participants           & 0.09        
                                                      & 0.20      \\
Average Number of Waves per Item                      & -0.20       
                                                      & 0.23      \\
Wave 1 (Decade)                                       & -1.17^{**}  
                                                      & 0.44      \\
Panels: BHPS                                          & 0.08        
                                                      & 0.05      \\
Panels: GSS                                           & 0.04        
                                                      & 0.05      \\
Panels: HILDA                                         & 0.08        
                                                      & 0.05      \\
Panels: PSID                                          & 0.09^{*}    
                                                      & 0.04      \\
Panels: SHP                                           & 0.06        
                                                      & 0.05      \\
Panels: SOEP                                          & 0.06        
                                                      & 0.05      \\
Panels: UKHLS                                         & 0.09        
                                                      & 0.06      \\
Topics: Environment and Climate                       & 0.04^{**}   
                                                      & 0.01      \\
Topics: Gender and Family                             & 0.00        
                                                      & 0.01      \\
Topics: Health and Morale                             & 0.03^{**}   
                                                      & 0.01      \\
Topics: National Identity, Ethnicity and Immigration  & 0.02        
                                                      & 0.01      \\
Topics: Occupation and Education                      & -0.02       
                                                      & 0.02      \\
Topics: Religion and Spirituality                     & -0.00       
                                                      & 0.01      \\
Topics: Social Life, Social Cohesion and Trust        & 0.03^{***}  
                                                      & 0.01      \\
Topics: Subjective SES                                & 0.03^{*}    
                                                      & 0.01      \\
\hline
Adjusted R-Squared                                    & 0.77 &    \\
\hline
\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}. N = 609.}
\end{tabular}
\end{center}
\end{table}
